Material Methods

### 2020-04-17 doc/MatMeth.Rmd
started outline and more section

---
title: ''
date: '`r Sys.Date()`'
output:
  word_document:
    toc: yes
    toc_depth: '5'
  pdf_document:
    toc: yes
    toc_depth: '5'
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
bibliography: refs_Main_Report.bib
---

@@

```{r error.repeatbility, echo=FALSE}

@@

Repeatability was assessed by X (comparing mulitple counted images)

(the data from these scripts differed slightly in that the total sc script returned the skeletonized SC area for the whole cell. <state the script parameters, (morphogy (3) and other parameter)>

Single bivalent features were measured both manual and with an automated image analysis software [@peterson2019]

DMC1 -- leptotene and sygotene cells were identified by SC morphology (by degree of synapsis) (cite another paper?). foci counted manually, error ccalulated from a subset of cells counted twice (supplement)

total number of DMC1 foci per cell were reported.

## Statisical Analysis

@@

@@

### Models

@@

## Single bivalent charaecterization

>>>>

---
title: ''
date: '`r Sys.Date()`'
output:
  html_document:
    toc: yes
    toc_depth: '5'
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '5'
  word_document:
    toc: yes
    toc_depth: '5'
bibliography: refs_Main_Report.bib
---

@@

```{r Image.profile, echo=FALSE}

# microscope
# cell certeria

@@

## Analysis

### DMC1

```{r DMC1.section.outline, echo=FALSE, include=FALSE}
#cell certeria, number, t.test
#DMC1 -- leptotene and sygotene cells were identified by SC morphology (by degree of synapsis) (cite another paper?). foci counted manually, error ccalulated from a subset of cells counted twice (supplement)
```

<certeria for DMC1 stained cells (single cells) SC morphology used for staging.>
<subset of males from strains were used>

A subset of strains, *musculus^PWD^*, *musculus^MSM^*, *domesticus^WSB^*, and *domesticus^G^* were quantified for DMC1.  A total of `r length( (DMC1.DF %>% filter(stage == "Z"))$Original.Name)` and `r length( (DMC1.DF %>% filter(stage == "L"))$Original.Name)` of zygotene and leptotene cells were quantified respectively.

### MLH1

@@

```{r MLH1.analysis, echo=FALSE, include=FALSE}

@@

@@

### Single bivalent charaecterization

```{r single.biv.chr, echo=FALSE, include=FALSE}
